---
title: "Annotations_Ontology"
author: "Sarah Arcos"
date: "10/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(clusterProfiler)
library(org.Hs.eg.db)
library(UpSetR)
library(DOSE)
library(Cairo)
```

## Load in CHIKV datasets
 - Filter for significant proteins
 - Select only protein accession column

```{r, message = FALSE}
hour0_minus <- read_tsv("0hr, -IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour1_minus <- read_tsv("1hr, -IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour3_minus <- read_tsv("3hr, -IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour0_plus <- read_tsv("0hr, +IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour1_plus <- read_tsv("1hr, +IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour3_plus <- read_tsv("3hr, +IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

all_chikv_list <- list(
  hour0_minus = hour0_minus$Proteins,
  hour1_minus = hour1_minus$Proteins,
  hour3_minus = hour3_minus$Proteins,
  hour0_plus = hour0_plus$Proteins,
  hour1_plus = hour1_plus$Proteins,
  hour3_plus = hour3_plus$Proteins
)

all_chikv <- bind_rows(list("0hr, -IFN" = hour0_minus, 
                              "1hr, -IFN" = hour1_minus, 
                              "3hr, -IFN" = hour3_minus, 
                              "0hr, +IFN" = hour0_plus, 
                              "1hr, +IFN" = hour1_plus, 
                              "3hr, +IFN" = hour3_plus), 
                         .id = "source")
```

## PRRs

```{r}
prrs <- read_tsv("/Users/saraharcos/Desktop/Nucleic acid sensor in viral immunity.txt")


chikv_prrs <- prrs %>%
  dplyr::select(`RNA sensor (PMID: 29677479)`, `Uniprot ID`) %>%
  left_join(all_chikv, by = c("Uniprot ID" = "Proteins")) %>%
  dplyr::select(`RNA sensor (PMID: 29677479)`, `Uniprot ID`, source) %>%
  filter(!is.na(source)) %>%
  mutate(exists = "X") %>%
  spread(source, exists)
```



## UpSet plot

```{r fig.width = 12, fig.height = 6}
upset_frame <- all_chikv %>%
  dplyr::select(source, Proteins) %>%
  mutate(exists = 1) %>%
  group_by(Proteins) %>%
  spread(source, exists, fill = 0)

inputData <- as.data.frame(upset_frame)
inputData$Proteins <- as.factor(inputData$Proteins)

#Define queries for plus IFN and minus IFN. Note that some intersections = 0, so will not be included in query list.

queries <- list(list(query = intersects, params = list("3hr, +IFN", "1hr, +IFN", "0hr, +IFN"), active = T, color = "#fc8d59"),
                     list(query = intersects, params = list("3hr, +IFN", "1hr, +IFN"), active = T, color = "#fc8d59"),
                     list(query = intersects, params = list("1hr, +IFN", "0hr, +IFN"), active = T, color = "#fc8d59"),
                     list(query = intersects, params = list("3hr, +IFN", "0hr, +IFN"), active = T, color = "#fc8d59"),
                     list(query = intersects, params = list("3hr, +IFN"), active = T, color = "#fc8d59", query.name = "+ IFN intersections"),
                     list(query = intersects, params = list("1hr, +IFN"), active = T, color = "#fc8d59"),
                     list(query = intersects, params = list("0hr, +IFN"), active = T, color = "#fc8d59"),
                     list(query = intersects, params = list("3hr, -IFN", "1hr, -IFN", "0hr, -IFN"), active = T, color = "#91bfdb"),
                     list(query = intersects, params = list("3hr, -IFN", "1hr, -IFN"), active = T, color = "#91bfdb"),
                     list(query = intersects, params = list("3hr, -IFN", "0hr, -IFN"), active = T, color = "#91bfdb"),
                     list(query = intersects, params = list("0hr, -IFN", "1hr, -IFN"), active = T, color = "#91bfdb"),
                     list(query = intersects, params = list("3hr, -IFN"), active = T, color = "#91bfdb"),
                     list(query = intersects, params = list("1hr, -IFN"), active = T, color = "#91bfdb"),
                     list(query = intersects, params = list("0hr, -IFN"), active = T, color = "#91bfdb", query.name = "- IFN intersections"))


upset_plot <- upset(inputData, nsets = 6, 
      order.by = c("freq"), 
      sets = c("0hr, -IFN", "1hr, -IFN", "3hr, -IFN", "0hr, +IFN", "1hr, +IFN", "3hr, +IFN"),
      query.legend = "top",
      queries = queries,
      keep.order = TRUE,
      text.scale = 2,
      sets.bar.color = "#999999",
      mainbar.y.label = "Intersection Size",
      sets.x.label = "Proteins Per Condition",
      line.size = 0.8,
      point.size = 3,
      mb.ratio = c(0.65, 0.35))

upset_plot
```




## Create enrichGO object
 - Use "simplify" function to collapse similar GO terms

```{r, fig.width = 10, fig.height = 8}
hour0_minus_MF <- enrichGO(gene     = hour0_minus$Proteins,
                OrgDb         = org.Hs.eg.db,
                keyType       = 'UNIPROT',
                ont           = "MF",
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.01,
                qvalueCutoff  = 0.01,
                readable = TRUE) %>%
  clusterProfiler::simplify()

hour0_minus_BP <- enrichGO(gene     = hour0_minus$Proteins,
                OrgDb         = org.Hs.eg.db,
                keyType       = 'UNIPROT',
                ont           = "BP",
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.01,
                qvalueCutoff  = 0.01,
                readable = TRUE)

hour0_minus_BP_simplified <- clusterProfiler::simplify(hour0_minus_BP)

cnetplot(hour0_minus_BP, showCategory = 10)

#dotplot(hour0_minus_MF, showCategory=30)

p2 <- cnetplot(hour0_minus_MF, showCategory = 5)
p2
#cowplot::plot_grid(p1, p2, ncol=2, labels=LETTERS[1:2])


```

## compareClusters

```{r, fig.width = 10}
chikv_MF <- compareCluster(all_chikv_list, fun = "enrichGO",
                           OrgDb = org.Hs.eg.db,
                           keyType       = 'UNIPROT',
                           ont           = "MF",
                           pAdjustMethod = "BH",
                           pvalueCutoff  = 0.01,
                           qvalueCutoff  = 0.05,
                           readable = TRUE)

chikv_MF_simplified <- clusterProfiler::simplify(chikv_MF)
print("done simplifying MF")

chikv_mf_summary <- data.frame(chikv_MF_simplified)
# dotplot(chikv_MF, showCategory = 8)

#mf <- dotplot(chikv_MF_simplified)

#ggsave("Figures/clusterProfiler_figs/mf.png", plot = mf, width = 8)

chikv_BP <- compareCluster(all_chikv_list, fun = "enrichGO",
                            OrgDb = org.Hs.eg.db,
                            keyType       = 'UNIPROT',
                            ont           = "BP",
                            pAdjustMethod = "BH",
                            pvalueCutoff  = 0.01,
                            qvalueCutoff  = 0.05,
                            readable = TRUE)
 
#dotplot(chikv_BP, showCategory = 8)
print("simplifying BP")
chikv_BP_simplified <- clusterProfiler::simplify(chikv_BP)

#bp <- dotplot(chikv_BP_simplified)

#ggsave("Figures/clusterProfiler_figs/bp.pdf", plot = bp, width = 10)

chikv_CC <- compareCluster(all_chikv_list, fun = "enrichGO",
                            OrgDb = org.Hs.eg.db,
                            keyType       = 'UNIPROT',
                            ont           = "CC",
                            pAdjustMethod = "BH",
                            pvalueCutoff  = 0.01,
                            qvalueCutoff  = 0.05,
                            readable = TRUE)
 
#dotplot(chikv_CC, showCategory = 8)
print("simplifying CC")
chikv_CC_simplified <- clusterProfiler::simplify(chikv_CC)
print("done simplifying CC")
#cc <- dotplot(chikv_CC_simplified)

#ggsave("Figures/clusterProfiler_figs/cc.pdf", plot = cc)

# make plots

CairoPDF(7, 10, file="chikv_mf.pdf", bg="transparent")
dotplot(chikv_MF_simplified)
dev.off()

# p1 <- dotplot(chikv_MF_simplified)
# 
# ggsave(filename = "chikv_mf.pdf",
#        plot = p1,
#        device = cairo_pdf())

CairoPDF(8.75, 10, file="chikv_bp.pdf", bg="transparent")
dotplot(chikv_BP_simplified)
dev.off()

CairoPDF(5.65, 10, file="chikv_cc.pdf", bg="transparent")
dotplot(chikv_CC_simplified)
dev.off()


get_entrez <- function(dataset){
  dataset %>%
  filter(!(Proteins %in% c("Capsid", "E1", "E2", "nsP1", "nsP2", "P13717", "Q6ZSR9", "Q58FF8"))) %>%
  pull(Proteins) %>%
  bitr(fromType = "UNIPROT", toType = "ENTREZID", OrgDb = "org.Hs.eg.db") %>%
  dplyr::select(ENTREZID)
}

all_chikv_list_entrez <- list(
  hour0_minus = get_entrez(hour0_minus)$ENTREZID,
  hour1_minus = get_entrez(hour1_minus)$ENTREZID,
  hour3_minus = get_entrez(hour3_minus)$ENTREZID,
  hour0_plus = get_entrez(hour0_plus)$ENTREZID,
  hour1_plus = get_entrez(hour1_plus)$ENTREZID,
  hour3_plus = get_entrez(hour3_plus)$ENTREZID
)


chikv_kegg <- compareCluster(geneCluster = all_chikv_list_entrez, fun = "enrichKEGG", organism = 'hsa', pvalueCutoff = 0.01)

get_symbol <- function(gene_ids){
  gene_ids %>% stringr:: str_split("/") %>% pluck(1) %>%
    glimpse() %>%
    bitr(fromType = "ENTREZID", toType = "SYMBOL", OrgDb = "org.Hs.eg.db") %>%
    pull(SYMBOL) %>%
    paste(collapse = "/")
}

test <- data.frame(chikv_kegg) %>%
  mutate(geneID = purrr::map_chr(geneID, get_symbol))

write.xlsx(test, file = "Final Tables/MaxQuant Final/kegg_genesymbols.xlsx", row.names=FALSE)


library(openxlsx)

datasets <- list(
  "Molecular function" = data.frame(chikv_MF_simplified),
  "Biological Process" = data.frame(chikv_BP_simplified),
  "Cellular Component" = data.frame(chikv_CC_simplified),
  "KEGG Pathways" = data.frame(chikv_kegg)
)
write.xlsx(datasets, file="Final Tables/MaxQuant Final/functional_analyses.xlsx", row.names=FALSE)

```

## RBP Analysis

```{r, message = FALSE}
gerstberger <- read_csv("Annotations/Gerstberger_Uniprot.csv") %>%
  filter(Status == "reviewed") %>%
  dplyr::select("Accession" = Entry)

go_rbp <- read_tsv("Annotations/RNA_binding_GO_050318.txt", col_names = c("Accession", "Name"))
go_rbp$Accession <- gsub(pattern = "UniProtKB\\:", go_rbp$Accession, replacement = "")
go_rbp$Name = NULL

castello <- read_csv("Annotations/HeLaInteractome_uniprot.csv", col_names = "Accession")

baltz <- read_csv("Annotations/Baltz_uniprot.csv") %>%
  dplyr::select(Accession = Entry)

known_rbps <- bind_rows(list("Gerstberger" = gerstberger,
                             "Castello" = castello,
                             "Baltz" = baltz,
                             "GO" = go_rbp),
                        .id = "Source") %>%
  unique()

all_chikv_annotation <- all_chikv %>%
  mutate(Annotation = case_when(
           Proteins %in% known_rbps$Accession ~ "Known",
           TRUE ~ "Novel"),
         source = factor(source, levels = c("0hr, -IFN", "1hr, -IFN", "3hr, -IFN", "0hr, +IFN", "1hr, +IFN", "3hr, +IFN")))

colors <- c("#d9d9d9", "#7fbf7b")

annotation_plot <- ggplot(all_chikv_annotation, aes(x = source, fill = Annotation)) +
  scale_fill_manual(values = colors) +
  geom_bar(position = "fill") +
  theme_minimal()
  #theme(panel.grid = element_blank())

annotation_plot
#ggsave("Figures/clusterProfiler_figs/tbps.pdf", plot = annotation_plot)
```

## ISG Analysis (downloaded from interferome.org on 10/07/19)

```{r}
#write all chikv proteins to a single file for interferome
all_chikv_ensembl <- all_chikv %>% 
  pull(Proteins) %>%
  bitr(fromType = "UNIPROT", toType = "ENSEMBL", OrgDb="org.Hs.eg.db")


all_chikv_ensembl %>%
  write_tsv("Annotations/all_chikv_100719.tsv", col_names = FALSE)

all_isgs <- all_chikv_ensembl %>%
  semi_join(read_tsv("Annotations/interferome_all_100719.txt", skip = 18), by = c("ENSEMBL" = "Ensembl Id"))

type1_isgs <- all_chikv_ensembl %>%
  semi_join(read_tsv("Annotations/interferome_type1_100719.txt", skip = 18), by = c("ENSEMBL" = "Ensembl Id"))

#NAs generated for chikv proteins and unmappable proteins to ensembl id (random unclassified proteins)
#Best to remove so they aren't counted as ISG or non-ISG
chikv_all_isgs <- all_chikv %>%
  mutate(ISG = case_when(
    Proteins %in% all_isgs$UNIPROT ~ "ISG",
    TRUE ~ "non-ISG"
  ))


chikv_type1 <- all_chikv %>%
  mutate(ISG = case_when(
    Proteins %in% type1_isgs$UNIPROT ~ "ISG",
    TRUE ~ "non-ISG"))

chikv_type1_byrbp <- all_chikv_annotation %>%
  mutate(ISG = case_when(
           Proteins %in% type1_isgs$UNIPROT ~ "ISG",
           TRUE ~ "non-ISG"),
    ISG_RBP = paste(ISG, Annotation, sep = " + "),
    ISG_RBP = factor(ISG_RBP, levels = c("non-ISG + Known", "ISG + Known", "non-ISG + Novel", "ISG + Novel")))

colors <- c("#d9d9d9", "#f4a582")

all_isg_plot <- ggplot(chikv_all_isgs, aes(x = source, fill = forcats::fct_rev(ISG))) +
  scale_fill_manual(values = colors) +
  geom_bar(position = "fill") +
  theme_minimal() +
  theme(axis.text = element_text(size = 20))

all_isg_plot

#ggsave("Figures/clusterProfiler_figs/all_isg.pdf", plot = all_isg_plot)

type1_isg_plot <- ggplot(chikv_type1_byrbp, aes(x = source, fill = forcats::fct_rev(ISG))) +
  scale_fill_brewer(palette = "Greys") +
  geom_bar(position = "fill") +
  theme_minimal() +
  theme(axis.text = element_text(size = 20))

type1_isg_plot

#ggsave("Figures/clusterProfiler_figs/type1_isg.pdf", plot = type1_isg_plot)

type1_isg_byrbp_plot <- ggplot(chikv_type1_byrbp, aes(x = source, fill = ISG_RBP)) +
  scale_fill_brewer(palette = "Paired") +
  geom_bar(position = "fill") +
  theme_minimal() +
  theme(axis.text = element_text(size = 20))

type1_isg_byrbp_plot

ggsave("Figures/clusterProfiler_figs/type1_isg_byrbp.pdf", plot = type1_isg_byrbp_plot)

```

## ggraph testing

```{r, fig.height = 15, fig.width = 20}

library(igraph)




term2gene <- all_chikv %>%
  dplyr::select(source, Proteins)

full_chikv <- all_chikv$Proteins %>%
  unique()

test <-enricher(full_chikv, TERM2GENE = term2gene)


cnetplot(test)



test <- as_tbl_graph(term2gene)

test_minus <- term2gene %>%
  filter(str_detect(source, "-IFN")) %>%
  as_tbl_graph()

test_minus_tbl <- term2gene %>%
  filter(str_detect(source, "-IFN"))

size <- sapply(all_chikv_list, length)
  V(test)$size <- min(size)/2
  
n <- length(all_chikv_list)
    V(test)$size[1:n] <- size
    
V(test)$color <- "#B3B3B3"
V(test)$color[1:n] <- "#E5C494"

test %>% 
    ggraph(layout = 'kk') + 
    geom_edge_link(edge_alpha = 0.5) + 
    geom_node_point(aes_(color=~I(color), size=~size)) +
    geom_node_text(aes_(label=~name), repel=TRUE) + 
    #ggtitle('Joining graphs') + 
    #theme_graph() +
    theme_void() +
    scale_size(range=c(3, 10), breaks=unique(round(seq(min(size), max(size), length.out=4))))

minus_chikv_list <- list(
  hour0_minus = hour0_minus$Proteins,
  hour1_minus = hour1_minus$Proteins,
  hour3_minus = hour3_minus$Proteins
)

test_minus <- term2gene %>%
  filter(str_detect(source, "-IFN")) %>%
  as_tbl_graph()

test_minus_tbl <- term2gene %>%
  filter(str_detect(source, "-IFN"))

size <- sapply(minus_chikv_list, length)
  V(test_minus)$size <- min(size)/2
  
n <- length(minus_chikv_list)
    V(test_minus)$size[1:n] <- size
    
test_minus_tbl <- setNames(test_minus_tbl$Proteins, test_minus_tbl$source)

V(test_minus)$color <- "#B3B3B3"
V(test_minus)$color[1:n] <- "#E5C494"
E(test_minus)$category <- rep(names(test_minus_tbl), sapply(test_minus_tbl, length))

test_minus %>% 
    ggraph(layout = 'kk') + 
    geom_edge_link(aes_(color = ~category), edge_alpha=.8) + 
    geom_node_point(aes_(color=~I(color), size=~size)) +
    geom_node_text(aes_(label=~name), repel=TRUE) + 
    #ggtitle('Joining graphs') + 
    #theme_graph() +
    theme_void() +
    scale_size(range=c(3, 10), breaks=unique(round(seq(min(size), max(size), length.out=4))))




plus_chikv_list <- list(
  hour0_plus = hour0_plus$Proteins,
  hour1_plus = hour1_plus$Proteins,
  hour3_plus = hour3_plus$Proteins
)

test_plus <- term2gene %>%
  filter(str_detect(source, "\\+IFN")) %>%
  as_tbl_graph()

test_plus_genes <- term2gene %>%
  filter(str_detect(source, "\\+IFN"),
         !(Proteins %in% c("Capsid", "E1", "E2", "nsP1", "nsP2", "P13717", "Q6ZSR9", "Q58FF8"))) %>%
  pull(Proteins) %>%
  unique() %>%
  bitr(test_plus, fromType = "UNIPROT", toType = "SYMBOL", OrgDb = "org.Hs.eg.db")

test_plus <- term2gene %>%
  filter(str_detect(source, "\\+IFN")) %>%
  left_join(test_plus_genes, by = c("Proteins" = "UNIPROT")) %>%
  select(source, SYMBOL) %>%
  as_tbl_graph()

test_plus_tbl <- term2gene %>%
  filter(str_detect(source, "\\+IFN"))

size <- sapply(plus_chikv_list, length)
  V(test_plus)$size <- min(size)/2
  
n <- length(plus_chikv_list)
    V(test_plus)$size[1:n] <- size
    
test_plus_tbl <- setNames(test_plus_tbl$Proteins, test_plus_tbl$source)

V(test_plus)$color <- "#B3B3B3"
V(test_plus)$color[1:n] <- "#E5C494"
E(test_plus)$category <- rep(names(test_plus_tbl), sapply(test_plus_tbl, length))

test_plus %>% 
    ggraph(layout = 'kk') + 
    geom_edge_link(aes_(color = ~category), edge_alpha=.8) + 
    geom_node_point(aes_(color=~I(color), size=~size)) +
    geom_node_text(aes_(label=~name), repel=TRUE) + 
    #ggtitle('Joining graphs') + 
    #theme_graph() +
    theme_void() +
    scale_size(range=c(3, 10), breaks=unique(round(seq(min(size), max(size), length.out=4))))
```




## Disease analysis
 - Need to convert IDs using bitr

```{r}
hour0_minus_entrez <- hour0_minus %>%
  filter(!(Proteins %in% c("Capsid", "E1", "E2", "nsP1", "nsP2", "P13717", "Q6ZSR9"))) %>%
  pull(Proteins) %>%
  bitr(fromType = "UNIPROT", toType = "ENTREZID", OrgDb = "org.Hs.eg.db") %>%
  dplyr::select(ENTREZID)

hour0_minus_do <- enrichDGN(gene = hour0_minus_entrez %>% pull(ENTREZID),
         #ont           = "DGN",
           pvalueCutoff  = 0.05,
           pAdjustMethod = "BH",
           qvalueCutoff  = 0.05,
           readable      = FALSE)
dotplot(hour0_minus_do)
```

## KEGG
```{r}
hour0_minus_kegg <- enrichKEGG(gene         = hour0_minus_entrez$ENTREZID,
                 organism     = 'hsa',
                 pvalueCutoff = 0.01)

dotplot(hour0_minus_kegg)


get_entrez <- function(dataset){
  dataset %>%
  filter(!(Proteins %in% c("Capsid", "E1", "E2", "nsP1", "nsP2", "P13717", "Q6ZSR9", "Q58FF8"))) %>%
  pull(Proteins) %>%
  bitr(fromType = "UNIPROT", toType = "ENTREZID", OrgDb = "org.Hs.eg.db") %>%
  dplyr::select(ENTREZID)
}

all_chikv_list_entrez <- list(
  hour0_minus = get_entrez(hour0_minus)$ENTREZID,
  hour1_minus = get_entrez(hour1_minus)$ENTREZID,
  hour3_minus = get_entrez(hour3_minus)$ENTREZID,
  hour0_plus = get_entrez(hour0_plus)$ENTREZID,
  hour1_plus = get_entrez(hour1_plus)$ENTREZID,
  hour3_plus = get_entrez(hour3_plus)$ENTREZID
)


chikv_kegg <- compareCluster(geneCluster = all_chikv_list_entrez, fun = "enrichKEGG", organism = 'hsa', pvalueCutoff = 0.01)

dotplot(chikv_kegg)


CairoPDF(7, 10, file="chikv_kegg.pdf", bg="transparent")
dotplot(chikv_kegg)
dev.off()
```


## PFAM domains (from david)

```{r, fig.width = 10}
#Try again using combined known and novel protein lists
all_chikv_annotation %>% filter(Annotation == "Novel" & !is.na(Proteins)) %>%
  dplyr::select(Proteins) %>%
  unique() %>%
  write_tsv("Annotations/GO inputs/DAVID_Interpro/all_novel.txt")

all_chikv_annotation %>% filter(Annotation != "Novel" & !is.na(Proteins)) %>%
  dplyr::select(Proteins) %>%
  unique() %>%
  write_tsv("Annotations/GO inputs/DAVID_Interpro/all_known.txt")

all_pfam <- bind_rows("Known" = read_tsv("Annotations/GO inputs/DAVID_Interpro/known_pfam_101019.txt"),
                          "Novel" =read_tsv("Annotations/GO inputs/DAVID_Interpro/novel_pfam_101019.txt"),
                          .id = "Annotation") %>%
  group_by(Annotation) %>%
  top_n(n = -15, wt = Benjamini) %>%
  filter(Benjamini < 0.05) %>%
  arrange(desc(Benjamini)) %>%
  ungroup() %>%
  mutate(Term = str_remove(Term, "PF[0-9]*:"),
         Term = forcats::fct_inorder(factor(Term)))

pfam_plot <- ggplot(all_pfam, aes(x = Annotation, y = Term, color = Benjamini, size = Count)) +
  geom_point() +
  facet_wrap(~Annotation, scales = "free", ncol = 2) +
  scale_color_gradient(low = "red", high = "blue") +
  scale_y_discrete(labels = function(y) str_wrap(y, width = 50)) +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 10, angle = 30, hjust = 1, vjust = 1),
        axis.text.y = element_text(size = 12),
        strip.text.x = element_text(size = 14),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        axis.line = element_line(colour = "black"))

pfam_plot

CairoPDF(15, 10, file="chikv_pfam.pdf", bg="transparent")
pfam_plot
dev.off()
```
##Overlap between previous siRNA screen for CHIKV-modulating factors
- CHIKV "A human genome-wide loss-of-function screen identifies effective chikungunya antiviral drugs", Karlas et al, 2016, Nature communications
- VEEV "siRNA Screen Identifies Trafficking Host Factors that Modulate Alphavirus Infection", Radoshitzky et al, 2016, PLOS pathogens
- SINV "Genome-Wide RNAi Screen Identifies Novel Host Proteins Required for Alphavirus Entry", Ooi et al, 2013, PLOS pathogens
- CHIKV **overexpression "A diverse range of gene products are effectors of the type I interferon antiviral response", Schoggins et al, 2011, Nature

```{r}
#Read in different data sets and annotate with source info


karlas_proviral <- read_csv("Annotations/Karlas_2016_proviral.csv", col_names = "Entry") %>%
  mutate(Source = "Karlas Proviral") %>%
  dplyr::select(Entry, Source)

karlas_antiviral <- read_csv("Annotations/Karlas_2016_antiviral.csv", col_names = "Entry") %>%
  mutate(Source = "Karlas Antiviral") %>%
  dplyr::select(Entry, Source)

radoshitzky <- read_csv("Annotations/radoshitzky_2016.csv") %>%
  mutate(Source = "Radoshitzky Antviral") %>%
  dplyr::select(Entry, Source)

Ooi_proviral <- read_csv("Annotations/Ooi_2013_proviral.csv") %>%
  mutate(Source = "Ooi Proviral") %>%
  dplyr::select(Entry, Source)

Ooi_antiviral <- read_csv("Annotations/Ooi_2013_antiviral.csv") %>%
  mutate(Source = "Ooi Antiviral") %>%
  dplyr::select(Entry, Source)

schoggins_overexpression <- read_csv("Annotations/Schoggins_2011_overexpression.csv") %>%
  mutate(Source = paste("Schoggins", effect, sep = " ")) %>%
  dplyr::select(Entry, Source)

screen_data <- bind_rows(karlas_proviral, karlas_antiviral, radoshitzky, Ooi_proviral, Ooi_antiviral, schoggins_overexpression)


#Compare to VIR-CLASP dataset
chikv_screened <- all_chikv %>%
  left_join(screen_data, by = c("Proteins" = "Entry")) %>%
  dplyr::select(Proteins, Condition = source,Source) %>%
  filter(!is.na(Source))

names <- bitr(chikv_screened$Proteins, fromType = "UNIPROT", toType = "SYMBOL", OrgDb = "org.Hs.eg.db")

chikv_screened %>%
  left_join(names, by = c("Proteins" = "UNIPROT")) %>%
  dplyr::select(Proteins, `Gene Symbol` = SYMBOL, Condition, Source) %>%
  mutate(exists = "X") %>%
  spread(Source, exists, fill = " ") %>%
  write.xlsx(file = "Final Tables/MaxQuant Final/screens.xlsx")

```

##Supplementary Table generation for siRNA screen analysis

```{r}
sup_table_screens <- virclasp %>%
  ungroup() %>%
  filter(Accession %in% virclasp_screened$Entry) %>%
  full_join(virclasp_screened, by = c("Accession" = "Entry")) %>%
  mutate(Name = str_extract(Description, "GN=[a-zA-Z0-9]* ")) %>%
  mutate(Name = str_trim(gsub("GN=", "", Name))) %>%
  select(Accession, Name, Description, Source) %>%
  unique() %>%
  mutate(exists = "X") %>%
  spread(Source, exists, fill = "")

write_tsv(sup_table_screens, here("Final Tables", "Sup_Table_2.tsv"))
```

