---
title: "Heatmap_Correlations"
author: "Sarah Arcos"
date: "1/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(reshape2)
```

The goal of this Rmarkdown is to generate a heatmap of correlations between intensity log-ratios from VIR-CLASP replicates and conditions for CHIKV.

First, read in the data
```{r, message = FALSE}
all_chikv <- bind_rows(list("0hr, -IFN" = read_tsv("0hr, -IFN Results/Final_Results.tsv"), 
                              "1hr, -IFN" = read_tsv("1hr, -IFN Results/Final_Results.tsv"), 
                              "3hr, -IFN" = read_tsv("3hr, -IFN Results/Final_Results.tsv"), 
                              "0hr, +IFN" = read_tsv("0hr, +IFN Results/Final_Results.tsv"), 
                              "1hr, +IFN" = read_tsv("1hr, +IFN Results/Final_Results.tsv"), 
                              "3hr, +IFN" = read_tsv("3hr, +IFN Results/Final_Results.tsv")), 
                         .id = "source")
```

Then organize the data in a "wide" format to allow for calculating a correlation matrix
```{r}
chikv_wide <- all_chikv %>%
  #keep only proteins with computed values
  filter(!is.na(pvalue.adjust)) %>%
  #get necessary info
  dplyr::select(source, Proteins, logRatio.Replicate1, logRatio.Replicate2, logRatio.Replicate3) %>%
  #gather replicate info because we need individual identifiers for each sample for correlations
  gather(Replicate, logRatio, -source, -Proteins) %>%
  #add ordering variables for hour and add replicate info to source
  mutate(hour = str_sub(source, start = 1, end = 3),
         source = paste(source, str_sub(Replicate, start = -1), sep = ", Rep ")) %>%
  #order the data
  arrange(hour) %>%
  mutate(source = forcats::fct_inorder(factor(source))) %>%
  dplyr::select(-Replicate, -hour) %>%
  #fix NA encoding
  mutate(logRatio = ifelse(is.nan(logRatio), NA, logRatio)) %>%
  #spread
  spread(source, logRatio , fill = NA) %>%
  dplyr::select(-Proteins)

```

Then make a function to calculate and plot the correlations
```{r}
#Possible options for use that deal with NA with no error: "complete.obs", "na.or.complete", "pairwise.complete.obs"
plot_cor <- function(data, cor_param, use_param, plot_title = " "){
  
  cormat <- round(cor(data, method = cor_param,  use = use_param), 2)
  cormat[lower.tri(cormat)] <- NA
  melted_cormat_upper <- melt(cormat, na.rm = TRUE)

  ggplot(melted_cormat_upper, aes(x = Var2, y = Var1, fill = value)) +
    geom_tile(color = "white")+
    scale_fill_gradient(limits = c(0,1), low = "#f7f7f7", high = "#a50026",
                        space = "Lab", 
                        name="Pearson\nCorrelation") +
    theme_minimal()+ 
    theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 10, hjust = 1), text = element_text(family = "Helvetica"))+
    coord_fixed() +
    geom_text(aes(Var2, Var1, label = value), color = "black", size = 3, family = "Helvetica") +
    theme(axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank(),
    legend.justification = c(1, 0),
    legend.position = c(0.6, 0.7),
    legend.direction = "horizontal") +
    guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5)) +
    labs(title = plot_title)
}
```

Calculate and plot correlations pairwise for minus and plus IFN conditions
 - Leave NAs and use "pairwise-complete" because this is what would generate correlation coefficients that correspond directly to the scatterplots in the original figure.
 - Save to disk
```{r}
cor_by_cond <- function(condition){
  p <- chikv_wide %>%
    dplyr::select(contains(condition)) %>%
    plot_cor("pearson", "pairwise.complete.obs", plot_title = condition)
  ggsave(paste("Figures/Reviewer_Heatmaps/", condition, ".pdf", sep = ""), plot = p,
         width = 7, height = 7)
  p
}

cor_by_cond("+IFN")
cor_by_cond("-IFN")

```



Generate a heatmap for each hour
 - Leave NAs and use "pairwise-complete" because this is what would generate correlation coefficients that correspond directly to the scatterplots in the original figure.
```{r}
#Make vector of all conditions and add names
conditions <- c("0hr, +IFN", "1hr, +IFN", "3hr, +IFN",
                "0hr, -IFN", "1hr, -IFN", "3hr, -IFN")
conditions = set_names(conditions)

#call cor_by_cond on each element of conditions
map(conditions, cor_by_cond)

```


























