---
title: "MaxQuant_Analysis"
author: "Sarah Arcos"
date: "10/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(limma)
library(ggpubr)
```

#This markdown processes the peptides.txt output from MaxQuant to determine significantly enriched proteins from a VIR-CLASP experiment. 
 - Function definitions at the top of the document, analysis of CHIKV at the bottom
 - Functions with plot output are denoted by "_plot" in the function name
 - main function calls all processing steps, with dataset and name as input. Name is used to create a directory to store output ("name_Results/").
 - Generated output includes: scatterplot, semiquantitative matrix, summary tables
 - Plots are saved as .pdf, and output to markdown
 
 ##Future directions
  - Give the functions better names. 
  - Add .md so github rendering looks nice (but out of an abundance of caution regarding embargoes, will wait until after publication).
 
##Step 0: Read in files and perform pre-processing
 - dplyr::select relevant columns
 - Remove reverse sequences and potential contaminants (but preserve benzonase (NUCA_SERMA))
 - Clean protein names using regex from [Uniprot website](https://www.uniprot.org/help/accession_numbers)
 - Set 0 values to NA
 - Split into one tibble for each condition tested. I have tried analyzing every condition together in a giant tibble and it is a huge mess. Pipes are impossible to follow due to group() ungroup() operations.
 
```{r, message = FALSE, warning = FALSE}
peptides_full <- read_tsv("MaxQuant/peptides.txt") %>%
  dplyr::select(`Sequence`, Proteins, `Unique (Proteins)`, `Unique (Groups)`, `Leading razor protein`, contains("LFQ intensity")) %>%
  filter(`Unique (Proteins)` == "yes" &
           !str_detect(`Leading razor protein`, "REV") &
           !str_detect(`Leading razor protein`, "CON") |
           str_detect(`Proteins`, "SERMA")) %>%
  dplyr::select(-c("Unique (Proteins)", "Unique (Groups)", "Leading razor protein")) %>%
  mutate(Proteins = case_when(
    #Preserve naming of CHIKV proteins
    Proteins %in% c("Capsid", "E1", "E2", "nsP1", "nsP2") ~ Proteins,
    TRUE ~ str_extract(Proteins, "[OPQ][0-9][A-Z0-9]{3}[0-9]|[A-NR-Z][0-9]([A-Z][A-Z0-9]{2}[0-9]){1,2}")
  ))

peptides_full[peptides_full == 0] <- NA

pep_hour0_minus <- peptides_full %>%
  dplyr::select(`Sequence`, Proteins, contains("0hr_minus"), contains("no4SU_minus"))

pep_hour1_minus <- peptides_full %>%
  dplyr::select(`Sequence`, Proteins, contains("1hr_minus"), contains("no4SU_minus"))

pep_hour3_minus <- peptides_full %>%
  dplyr::select(`Sequence`, Proteins, contains("3hr_minus"), contains("no4SU_minus"))

pep_hour0_plus <- peptides_full %>%
  dplyr::select(`Sequence`, Proteins, contains("0hr_plus"), contains("no4SU_plus"))

pep_hour1_plus <- peptides_full %>%
  dplyr::select(`Sequence`, Proteins, contains("1hr_plus"), contains("no4SU_plus"))

pep_hour3_plus <- peptides_full %>%
  dplyr::select(`Sequence`, Proteins, contains("3hr_plus"), contains("no4SU_plus"))
```

##Main: call this function on each condition. Two arguments are the dataset (generated in above chunk) and a name (string) to use for that dataset in plots and output directory.
```{r, warning = FALSE}
main <- function(dataset, name) {
  
  #add check for existing directory later
  results_dir <- paste(name, " Results", sep = "")
  dir.create(results_dir)
  
  data_1 <- step1(dataset)
  
  data_3 <- data_1 %>%
    step2() %>%
    step3()
  
  quant <- data_3 %>%
    step4_plot(name, results_dir)
  
  semi_quant <- data_1 %>%
    step5() %>%
    step6() %>%
    step7_plot(name, results_dir) %>%
    step8()
  
  final_table <- data_3 %>%
    step9(quant, semi_quant, results_dir)
  
  print("Analysis Successful")
    
  step10(data_1, final_table, name)
}
```

##Step 1: Only consider proteins "with at least two quantified peptides" [CARIC paper](https://www.pnas.org/content/115/17/E3879)
 - After splitting into conditions above, some peptides might have all NAs, so need to remove. Achieve by calculating rowMeans with na.rm = T, then if the mean is still NA it means all NAs.
 - Count peptides to determine if at least two (> 1) quantified peptides
```{r}
step1 <- function(dataset){
  print("Executing Step 1")
  dataset %>%
    mutate(all_mean = rowMeans(.[,3:7], na.rm = T)) %>%
    filter(!is.na(all_mean)) %>%
    dplyr::select(-all_mean) %>%
    group_by(Proteins) %>%
    add_tally(name = "Count") %>%
    filter(Count > 1) %>%
    dplyr::select(-Count) %>%
    ungroup()
}

#step1_test <- step1(pep_hour0_plus)
```

##Step 2: Calculate peptide intensity ratios
 - Calculate mean intensity from no4SU samples (sample names differ so referring to these columns by index)
 - Remove individual no4SU replicates after mean is calculated
 - Calculate peptide intensity ratios, then log2
 - Also clean up sample names
```{r}
step2 <- function(dataset){
  print("Executing Step 2")
  dataset %>%
    mutate(ave_no4SU = rowMeans(.[,6:7], na.rm = T)) %>%
    dplyr::select(1:5, 8) %>%
    gather(Sample, Intensity, -Sequence, -Proteins, -ave_no4SU) %>%
    #clean up sample names and calculate log2 intensity ratios
    mutate(Sample = str_remove(Sample, "LFQ intensity "),
           log_intensity_ratio = log2(Intensity/ave_no4SU)) %>%
    dplyr::select(-ave_no4SU, -Intensity)
}

#step2_test <- step2(step1_test)
```

##Step 3: Calculate mean log ratio for each protein
 - Trimmed mean (20%): “The differential abundance of a protein group was estimated as the trimmed mean over all differential peptide abundance where 20% of the data are trimmed on both sides.” From [2012 Castello](https://www.sciencedirect.com/science/article/pii/S0092867412005764?via%3Dihub)
```{r}
step3 <- function(dataset){
  print("Executing Step 3")
  dataset %>%
    group_by(Proteins, Sample) %>%
    mutate(ave_log_ratio = mean(log_intensity_ratio, trim = 0.20, na.rm = TRUE)) %>%
    dplyr::select(-log_intensity_ratio, -Sequence) %>%
    unique()
}

#step3_test <- step3(step2_test)
```

##Step 4: Limma moderated t test
 - Calculate limma moderated t test (return value is tibble with results)
 - Generates 3 scatter plots (pairwise for the 3 replicates)
 - Plots saved to subdirectory "Quant_Scatters" in results directory
 - Significance cutoff is p.adjust < 0.01 and fold enrichment > 5
```{r}
step4_plot <- function(dataset, name, results_dir) {
  print("Executing Step 4")
  limma_data <- dataset %>%
    ungroup() %>%
    spread(Sample, ave_log_ratio) %>%
    column_to_rownames(var = "Proteins") %>%
    lmFit() %>%
    eBayes() %>%
    #I want all the data back. Filter by significance later
    topTable(number = Inf) %>%
    rownames_to_column(var = "Proteins")
  
  plot_data <- dataset %>%
    ungroup() %>%
    spread(Sample, ave_log_ratio) %>%
    left_join(limma_data, by = "Proteins") %>%
    #Add significance encoding
    mutate(Significant = case_when(
      adj.P.Val < 0.01 & AveExpr > (log2(5)) ~ "Yes",
      TRUE ~ "No"
    ))
  
  plot1 <- plot_fun(plot_data, 2, 3)
  plot2 <- plot_fun(plot_data, 2, 4)
  plot3 <- plot_fun(plot_data, 3, 4)
  
  figure <- ggarrange(plot1, plot2, plot3,
                    labels = c("A", "B", "C"),
                    ncol = 3, nrow = 1,
                    common.legend = TRUE, legend = "bottom")
  figure <- annotate_figure(figure, top = text_grob(name))
  
  print(figure)
  ggsave(paste(results_dir, "/Quant_Scatters.pdf", sep = ""), width = 12, height = 4)
  
  limma_data
}

#Plotting function
plot_fun <- function(dataset, var1, var2){
  dataset %>% 
    ggplot(aes(x = pull(dataset, var = var1), y = pull(dataset, var = var2), color = Significant)) +
      geom_point(alpha = 0.3) +
      geom_hline(yintercept = 0) +
      geom_hline(yintercept = 1, color = "darkgreen", linetype = "dashed", size = 0.5) +
      geom_vline(xintercept = 0) +
      geom_vline(xintercept = 1, color = "darkgreen", linetype = "dashed", size = 0.5) +
      scale_color_manual(values = c("black", "red")) +
      scale_x_continuous(breaks = c(0, 2, 4, 6, 8, 10), limits = c(-3, 10)) +
      scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10),  limits = c(-3, 10)) +
      theme_minimal() +
      labs(x = paste("Replicate ", var1-1, sep = ""), y = paste("Replicate ", var2-1, sep = ""))
}

#step4_test <- step4_plot(step3_test, "Name Test", results_dir = "Figures")
```
 
##Step 5: Count peptide occurrences
 - Remove peptides with all NAs (in dataset to begin with because original dataset included all conditions)
 - Add grouping variables (Sample, Condition)
 - Tally peptides by Sequence and Condition
 - Spread back to wide format and change NAs to 0.
```{r}
step5 <- function(dataset){
  print("Executing Step 5")
  temp <- dataset %>%
    gather(Sample, Intensity, -Proteins, -Sequence) %>%
    filter(!is.na(Intensity)) %>%
    mutate(Sample = str_remove(Sample, "LFQ intensity "),
          Condition = str_sub(Sample, start = 1, end = 5)
          ) %>%
    group_by(Sequence, Condition) %>%
    add_tally() %>%
    dplyr::select(-Sample, -Intensity) %>%
    unique() %>%
    spread(Condition, n)
  
  temp[is.na(temp)] <- 0
  
  temp
}

#step5_test <- step5(step1_test)
```

##Step 6: Assign significance for semi-quant
 - Don't need to do all matrix positions, just the likely ones (bottom left 2x2 square)
 - Matrix is based on  analysis from [Garcia-Moreno 2019](https://www.sciencedirect.com/science/article/pii/S1097276519300371?via%3Dihub) and [Sysoev 2016](https://www.nature.com/articles/ncomms12128)
 - Significance is for __peptides__ not the proteins. Protein "hit" determination comes later. Methods in above articles were kinda vague, but I went through the excel tables and they used peptides, not proteins to generate matrix.
 - Made a function to "add missing" to add back 0 tallies. There is probably a fancy dplyr way to do this but couldn't figure it out.
```{r}
step6 <- function(dataset){
  print("Executing Step 6")
  fdrs <- dataset %>%
    ungroup() %>%
    mutate(mat_pos = str_c(.[[3]], .[[4]], sep = ":")) %>%
    group_by(mat_pos) %>%
    tally() %>%
    add_missing() %>%
    spread(mat_pos, n) %>%
    gather(mat_pos, count, `3:0`, `3:1`, `2:0`, `2:1`) %>%
    mutate(FDR = case_when(
      mat_pos == "3:0" ~ `0:2`/count,
      mat_pos == "3:1" ~ `1:2`/count,
      mat_pos == "2:0" ~ `0:2`/count,
      mat_pos == "2:1" ~ `1:2`/count
    )) %>%
    dplyr::select(mat_pos, FDR)
  
  dataset %>%
    ungroup() %>%
    mutate(mat_pos = str_c(.[[3]], .[[4]], sep = ":")) %>%
    group_by(mat_pos) %>%
    add_tally(name = "mat_pos_count") %>%
    left_join(fdrs, by = "mat_pos") %>%
    mutate(SigCount = case_when(
      FDR < 0.01 ~ "Yes",
      TRUE ~ "No"
    ))
}

add_missing <- function(dataset){
  combinations <- crossing(plus = 0:3, minus = 0:2) %>%
    mutate(mat_pos = str_c(plus, minus, sep = ":")) %>%
    anti_join(dataset, by = "mat_pos") %>%
    mutate(n = 0) %>%
    dplyr::select(mat_pos, n) %>%
    bind_rows(dataset)
}

#step6_test <- step6(step5_test)
```

##Step7: Plot matrix with FDRs and coloring by significance
 - Plots the matrix based on description in the Sysoev methods.
 - Outputs plot to results directory with name SemiQuant_Matrix.pdf
 - Round the FDRs to 4 digits
```{r}
step7_plot <- function(dataset, name, results_dir) {
  print("Executing Step 7")
  temp <- dataset %>%
    ungroup() %>%
    dplyr::select(-1,-2,-5) %>%
    unique() %>%
    mutate(FDR = round(FDR, digits = 4),
           FDR = case_when(
             .[[1]] == 3 ~ str_c("FDR < ", FDR),
             TRUE ~ str_c("FDR = ", FDR)
           )) %>%
    mutate_all(as.factor) %>%
    ggplot(aes(x = pull(., var = 2), y = fct_rev(pull(., var = 1)), color = SigCount)) +
      geom_text(aes(label = mat_pos_count), size = 8) +
      geom_text(aes(label = FDR), size = 3, nudge_y = -0.3, show.legend = FALSE) +
      theme(panel.grid = element_blank()) +
    labs(x = "no4SU", y = "4SU", title = name)
  
  print(temp)
  ggsave(paste(results_dir, "/SemiQuant_Matrix.pdf", sep = ""))
  #returning input data for next processing steps
  dataset
}

#step7_test <- step7_plot(step6_test, "0hr, +IFN", "Figures")
```

##Step 8: Find significant proteins from significant peptides
 - Significance is based on square in matrix, and matrix contains _peptides_. So to determine if a _protein_ is significant, must test whether all peptides in the protein are in a significant _square in the matrix_, "Only proteins comprising peptides with FDR<0.01 were included in the Drosophila RNA interactome." From [Sysoev 2016](https://www.nature.com/articles/ncomms12128).
 - So, paste all sig results for the peptides in a protein. If there is a "No", it is not included.
```{r}
step8 <- function(dataset){
  print("Executing Step 8")
  dataset %>%
    ungroup() %>%
    group_by(Proteins) %>%
    mutate(sigTotal = paste(SigCount, collapse = "")) %>%
    mutate(SigCount = case_when(
      str_detect(sigTotal, "No") ~ "",
      TRUE ~ "Yes"
    )) %>%
    dplyr::select(Proteins, SigCount)
}

#step8_test <- step8(step7_test)
```

##Step 9: Compile final table
 - write to disk ("Final_Results.tsv)
 - Lots of formatting to make a nice Supplemental Table.
 - Make columns to identify which proteins were "significant" and by which method. Table format heavily inspired by Sysoev and Garcia-Moreno papers.
```{r}
step9 <- function(full_data, quant, semiquant, results_dir) {
  print("Executing Step 9")
  
  temp <- full_data %>%
    spread(Sample, ave_log_ratio) %>%
    full_join(quant, by = "Proteins") %>%
    full_join(semiquant, by = "Proteins") %>%
    mutate(SigQuant = case_when(
       adj.P.Val < 0.01 & AveExpr > (log2(5)) ~ "Yes",
       TRUE ~ "")
        ) %>%
    dplyr::select(Proteins, logRatio.Replicate1 = 2,
          logRatio.Replicate2 = 3,
          logRatio.Replicate3 = 4,
          logRatio.Average = AveExpr,
          pvalue = P.Value,
          pvalue.adjust = adj.P.Val,
          SigQuant = SigQuant,
          SigCount = SigCount,
          -B, -t, -logFC) %>%
    unique() %>%
    #If only one value, say not significant by quantitative method
    mutate(SigQuant = case_when(
      is.na(logRatio.Replicate1) & is.na(logRatio.Replicate2) ~ "",
      is.na(logRatio.Replicate1) & is.na(logRatio.Replicate3) ~ "",
      is.na(logRatio.Replicate2) & is.na(logRatio.Replicate3) ~ "",
      TRUE ~ SigQuant
    ))
  
  write_tsv(temp, paste(results_dir, "/Final_Results.tsv", sep = ""))
  
  temp
}

#step9_test <- step9(step3_test, step4_test, step8_test, "Figures")
```
 
##Step 10: Print results summary
 - Prints result summary to the markdown
```{r}
step10 <- function(data_1, final_data, name){
  print("Executing Step 10")
  
  start_count <- data_1 %>%
    dplyr::select(Proteins) %>%
    n_distinct()
  
  quant_count <- final_data %>%
    filter(SigQuant == "Yes") %>%
    n_distinct()
  
  semiquant_count <- final_data %>%
    filter(SigCount == "Yes") %>%
    n_distinct()
  
  print(paste("Number of proteins analyzed for ", name, ": ", start_count))
  print(paste("Number of significant proteins by quantitative method: ", quant_count))
  print(paste("Number of significant proteins by semiquantitative method: ", semiquant_count))
}
```

##Analyzing the conditions!

###0hr, -IFN
```{r, warning = FALSE}
main(pep_hour0_minus, "0hr, -IFN")
```

###1hr, -IFN
```{r, warning = FALSE}
main(pep_hour1_minus, "1hr, -IFN")
```

###3hr, -IFN
```{r, warning = FALSE}
main(pep_hour3_minus, "3hr, -IFN")
```

###0hr, +IFN
```{r, warning = FALSE}
main(pep_hour0_plus, "0hr, +IFN")
```

###1hr, +IFN
```{r, warning = FALSE}
main(pep_hour1_plus, "1hr, +IFN")
```

###3hr, +IFN
```{r, warning = FALSE}
main(pep_hour3_plus, "3hr, +IFN")
```



##Compile final large table for Supplement (with tabs)
 - get genenames with bitr function from clusterProfiler
 - Add column based on whether protein was found in virion
 - Formatting to improve readability, ie changing NA to " ".

```{r, message = FALSE, warning = FALSE}
library(openxlsx)
library(clusterProfiler)

hour0_minus <- read_tsv("0hr, -IFN Results/Final_Results.tsv")

hour1_minus <- read_tsv("1hr, -IFN Results/Final_Results.tsv")

hour3_minus <- read_tsv("3hr, -IFN Results/Final_Results.tsv")

hour0_plus <- read_tsv("0hr, +IFN Results/Final_Results.tsv")

hour1_plus <- read_tsv("1hr, +IFN Results/Final_Results.tsv")

hour3_plus <- read_tsv("3hr, +IFN Results/Final_Results.tsv")

#virion list
virion = read_tsv("virion_chikv_overlap.txt")

#Formating function. Run on each dataset
format_final <- function(dataset){
  names <- bitr(dataset$Proteins, fromType = "UNIPROT", toType = "SYMBOL", OrgDb = "org.Hs.eg.db")
  dataset[is.na(dataset)] <- "NA"
  
  dataset %>%
    left_join(names, by = c("Proteins" = "UNIPROT")) %>%
    mutate(`Gene Symbol` = case_when(
      is.na(SYMBOL) ~ Proteins,
      TRUE ~ SYMBOL),
      `Uniprot ID`= Proteins,
      SigCount = case_when(
        SigCount == "NA" ~ " ",
        TRUE ~ SigCount),
      SigQuant = case_when(
        SigQuant == "NA" ~ " ",
        TRUE ~ SigQuant),
      `In Virion` = case_when(
        `Uniprot ID` %in% virion$Proteins ~ "Yes",
        TRUE ~ " "
      )) %>%
    dplyr::select(`Gene Symbol`, `Uniprot ID`,
           logRatio.Replicate1,
          logRatio.Replicate2,
          logRatio.Replicate3,
          logRatio.Average,
          pvalue,
          pvalue.adjust,
          SigQuant,
          SigCount,
          `In Virion`)
}


datasets <- list(
  "0hr, -IFN" = format_final(hour0_minus),
  "1hr, -IFN" = format_final(hour1_minus),
  "3hr, -IFN" = format_final(hour3_minus),
  "0hr, +IFN" = format_final(hour0_plus),
  "1hr, +IFN" = format_final(hour1_plus),
  "3hr, +IFN" = format_final(hour3_plus)
)
write.xlsx(datasets, file="Final Tables/MaxQuant Final/chikv.xlsx", row.names=FALSE)
```
























