---
title: "Virion"
author: "Sarah Arcos"
date: "9/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


## Read in Virion peptides
 - Filter for "Unique (Proteins)" = yes
 - Also filter out CON and REV peptides
 - Can now remove "Unique (Proteins)", "Unique (Groups)", and "Leading razor protein columns".
 
```{r, message = FALSE}
virion_full <- read_tsv("Virion/peptides.txt") %>%
  select(`Sequence`, Proteins, `Unique (Proteins)`, `Unique (Groups)`, `Leading razor protein`, contains("Intensity"), -contains("LFQ")) %>%
  filter(Intensity > 0,
         `Unique (Proteins)` == "yes" &
         !str_detect(`Leading razor protein`, "REV") &
         !str_detect(`Leading razor protein`, "CON")) %>%
  select(-c("Unique (Proteins)", "Unique (Groups)", "Leading razor protein")) %>%
  mutate(Proteins = case_when(
    Proteins %in% c("E1", "E2", "Capsid", "nsP1", "nsP2", "nsP3") ~ Proteins,
    TRUE ~ str_extract(Proteins, "[OPQ][0-9][A-Z0-9]{3}[0-9]|[A-NR-Z][0-9]([A-Z][A-Z0-9]{2}[0-9]){1,2}")))

virion_full[virion_full == 0] <- NA

print(paste("Total unique proteins in unfiltered Virion: ", n_distinct(virion_full$Proteins)))


print(paste("Total unique peptides in unfiltered Virion: ", n_distinct(virion_full$Sequence)))
```

## Load in CHIKV VIR-CLASP

```{r, message = FALSE}
virclasp_full <- read_tsv("MaxQuant/peptides.txt") %>%
  select(`Sequence`, Proteins, `Unique (Proteins)`, `Unique (Groups)`, `Leading razor protein`, contains("Intensity"), -contains("LFQ")) %>%
    filter(`Unique (Proteins)` == "yes" &
           !str_detect(`Leading razor protein`, "REV") &
           !str_detect(`Leading razor protein`, "CON") |
           str_detect(`Proteins`, "SERMA")) %>%
  select(-c("Unique (Proteins)", "Unique (Groups)", "Leading razor protein")) %>%
  mutate(Proteins = str_extract(Proteins, "[OPQ][0-9][A-Z0-9]{3}[0-9]|[A-NR-Z][0-9]([A-Z][A-Z0-9]{2}[0-9]){1,2}"))

virclasp_full[virclasp_full == 0] <- NA

print(paste("Total unique proteins in unfiltered VIR-CLASP: ", n_distinct(virclasp_full$Proteins)))


print(paste("Total unique peptides in unfiltered VIR-CLASP: ", n_distinct(virclasp_full$Sequence)))
```

## Find peptides that exactly overlap

```{r}
shared_peptides <- virclasp_full %>%
  filter(Sequence %in% virion_full$Sequence)

print(paste("Total shared peptides between unfiltered VIR-CLASP and unfiltered Virion: ", n_distinct(shared_peptides$Sequence)))
```


## Count proteins that overlap (by shared peptide)

```{r}
print(paste("Total shared proteins between unfiltered VIR-CLASP and unfiltered Virion: ", n_distinct(shared_peptides$Proteins)))
```

## Now compare to filtered (real) VIR-CLASP list

```{r}

hour0_minus <- read_tsv("0hr, -IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour1_minus <- read_tsv("1hr, -IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour3_minus <- read_tsv("3hr, -IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour0_plus <- read_tsv("0hr, +IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour1_plus <- read_tsv("1hr, +IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

hour3_plus <- read_tsv("3hr, +IFN Results/Final_Results.tsv") %>%
  filter(SigCount == "Yes" | SigQuant == "Yes")

all_chikv <- bind_rows(list("0hr, -IFN" = hour0_minus, 
                              "1hr, -IFN" = hour1_minus, 
                              "3hr, -IFN" = hour3_minus, 
                              "0hr, +IFN" = hour0_plus, 
                              "1hr, +IFN" = hour1_plus, 
                              "3hr, +IFN" = hour3_plus), 
                         .id = "source")

n_distinct(all_chikv$Proteins)

virclasp_real <- all_chikv %>%
  filter(Proteins %in% shared_peptides$Proteins)

print(paste("Total shared proteins between real VIR-CLASP and unfiltered Virion: ", n_distinct(virclasp_real$Proteins)))


ggplot(virclasp_real, aes(x = source)) +
  geom_bar()

#Print accessions to text file
virclasp_real %>%
  select(Proteins) %>%
  unique() %>%
  write_tsv("virion_chikv_overlap.txt")

```

## Use only virion peptides that have intensity values in both replicates
 - Removes 8 proteins, not really worth it because it is harder to justify (and less conservative)
```{r}
virion_both <- virion_full %>%
  select(-Intensity) %>%
  gather(Sample, Intensity, -Sequence, -Proteins) %>%
  filter(!is.na(Intensity)) %>%
  mutate(exists = 1) %>%
  group_by(Sequence) %>%
  mutate(real = sum(exists)) %>%
  filter(real == 2)

shared_peptides_bothreps <- virclasp_full %>%
  filter(Sequence %in% virion_both$Sequence)

print(paste("Total shared peptides between unfiltered VIR-CLASP and both reps of Virion: ", n_distinct(shared_peptides_bothreps$Sequence)))

print(paste("Total shared proteins between unfiltered VIR-CLASP and both reps of Virion: ", n_distinct(shared_peptides_bothreps$Proteins)))


virclasp_real_bothreps <- all_chikv %>%
  filter(Proteins %in% shared_peptides_bothreps$Proteins)

print(paste("Total shared proteins between real VIR-CLASP and both reps of Virion: ", n_distinct(virclasp_real_bothreps$Proteins)))

virclasp_real_bothreps %>%
  select(Proteins) %>%
  unique() %>%
  write_tsv("virion_chikv_overlap_bothreps.txt")


```


